---
title: "Failure Relapse India, version 6"
author: "David Jenkins"
date: "11/5/2018"
output:
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
    theme: "flatly"
---

# Load Data

```{r load}
suppressPackageStartupMessages({
  library(singleCellTK)
  library(DT)
  library(ComplexHeatmap)
  library(TBSignatureProfiler)
  library(reshape2)
  library(RColorBrewer)
  library(ggplot2)
})

TBsignatures <- readRDS("~/git/TBSignatureProfiler/misc/TBsignatures_all.rds")

indata <- readRDS("failure_relapse_india_2018.rds")
indata <- indata[rowSds(assay(indata, "counts")) != 0,]
indata_subset <- indata[, colnames(indata) != "102-00107-A0"]
indata_subset <- indata_subset[rowSds(assay(indata_subset, "counts")) != 0,]
colData(indata)$visit_subjtype <- paste(as.character(colData(indata)$visit),
                                        as.character(colData(indata)$subjtype,
                                                     sep=" "))
colData(indata_subset)$visit_subjtype <- paste(as.character(colData(indata_subset)$visit),
                                               as.character(colData(indata_subset)$subjtype,
                                                            sep=" "))
colData(indata_subset)$Subject <- gsub("\\d$", "", colnames(indata_subset))
knitr::kable(table(colData(indata)[,c("visit", "subjtype")]))
```

# PCA Visualization

```{r pca}
plotPCA(indata, colorBy = "lane", shape = "visit", reducedDimName = "PCA_logtpm")
```

# Random Genes {.tabset}

## Full Data {.tabset}

### Housekeeping Control Genes

```{r housekeeping, fig.width=10}
colList <- list(visit = c("Baseline"="blue", "Month 2"="yellow"),
                subjtype = c("failure"="red", "Control"="grey"))
signatureGeneHeatmap(indata, "logtpm", c("GAPDH", "ACTB", "B2M", "HMBS", "PPIB", "TRAP1", "DECR1", "FPGS", "FARP1", "MAPRE2", "PEX16", "GINS2", "CRY2", "CSNK1G2", "A4GALT"),
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "Housekeeping Genes",
                     showRowNames = TRUE, scale=FALSE)
```

### 100 Genes

```{r 100g, fig.width=10}
colList <- list(visit = c("Baseline"="blue", "Month 2"="yellow"),
                subjtype = c("failure"="red", "Control"="grey"))
signatureGeneHeatmap(indata, "logtpm", sample(rownames(indata), 100),
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "100 Random genes",
                     showRowNames = FALSE)
```

### 500 Genes

```{r 500g, fig.width=10}
signatureGeneHeatmap(indata, "logtpm", sample(rownames(indata), 500),
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "500 Random genes",
                     showRowNames = FALSE)
```

### 1000 Genes

```{r 1000g, fig.width=10}
signatureGeneHeatmap(indata, "logtpm", sample(rownames(indata), 1000),
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "1000 Random genes",
                     showRowNames = FALSE)

signatureGeneHeatmap(indata, "logtpm", sample(rownames(indata), 1000),
                     annotationColNames = c("flowcell", "lane"),
                     name = "1000 Random genes",
                     showRowNames = FALSE)
```

## Subset Data (without 102-00107-A0) {.tabset}

### 100 Genes

```{r s100g, fig.width=10}
signatureGeneHeatmap(indata_subset, "logtpm", sample(rownames(indata_subset), 100),
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "100 Random genes",
                     showRowNames = FALSE)
```

### 500 Genes

```{r s500g, fig.width=10}
signatureGeneHeatmap(indata_subset, "logtpm", sample(rownames(indata_subset), 500),
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "500 Random genes",
                     showRowNames = FALSE)
```

### 1000 Genes

```{r s1000g, fig.width=10}
signatureGeneHeatmap(indata_subset, "logtpm", sample(rownames(indata_subset), 1000),
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "1000 Random genes",
                     showRowNames = FALSE)

signatureGeneHeatmap(indata_subset, "logtpm", sample(rownames(indata_subset), 1000),
                     annotationColNames = c("flowcell", "lane"),
                     name = "1000 Random genes",
                     showRowNames = FALSE)
```

### chrY Genes

```{r chryg}
chrygenes <- read.table("../20180725_latent_capetown_2018/chrygenes.txt",
                        stringsAsFactors = FALSE)
chrygenes <- chrygenes$V2
chrygenes <- chrygenes[chrygenes %in% rownames(indata_subset)]
bestygenes <- chrygenes[rowSds(assay(indata_subset, "logtpm")[chrygenes,]) > 1.5 &
                          rowSums(assay(indata_subset, "logtpm")[chrygenes,]) >
                          ncol(indata_subset)*.2]
signatureGeneHeatmap(indata_subset, "logcounts", sigGenes = bestygenes,
                     annotationColNames = c("sex", "visit_subjtype"),
                     scale=F, name = "Chromosome Y Genes", showColumnNames = FALSE)
```

### Most Variable Genes

```{r mostvar}
signatureGeneHeatmap(indata_subset, "logtpm", rownames(indata_subset)[order(matrixStats::rowVars(assay(indata_subset, "logtpm")), decreasing = TRUE)[1:500]],
                     annotationColNames = c("visit", "subjtype"),
                     colList = colList, name = "500 Most Variable",
                     showRowNames = FALSE)
```


# Diffex Baseline control vs failure {.tabset}

## Limma

```{r diffex_lim}
baseline_data <- indata_subset[,colData(indata_subset)$visit == "Baseline"]
baseline_data <- baseline_data[rowSds(assay(baseline_data, "counts")) != 0,]
baselineres <- scDiffEx(baseline_data, "logtpm", "subjtype",
                        ntop=nrow(baseline_data), usesig = FALSE,
         diffexmethod = "limma")

res <- lapply(colnames(colData(baseline_data)[,3:16]), function(x){
  return(scDiffEx(baseline_data, "logtpm", "subjtype",
           covariates = x,
           ntop=nrow(baseline_data), usesig = FALSE,
           diffexmethod = "limma"))
})
names(res) <- colnames(colData(baseline_data)[,3:16])
lapply(res, function(x){
  sum(x$padj < 0.05)
})
```

No significant genes found at FDR < 0.05 without covariates or with smoking status,
diabetes status, cough duration, random blood sugar, alcohol frequency, drinks
per day, alcuse, alc_score, diabetes, age, sex, riskyalc, time2pos_days, and
smear result as single covariates.

## DESeq2

```{r diffex_des}
colList_m <- list(visit = c("Baseline"="blue", "Month 2"="yellow"),
                  subjtype = c("failure"="red", "Control"="grey"),
                  totmiss = c("0"=brewer.pal(6, "Set1")[1],
                              "1"=brewer.pal(6, "Set1")[2],
                              "2"=brewer.pal(6, "Set1")[3],
                              "5"=brewer.pal(6, "Set1")[4],
                              "6"=brewer.pal(6, "Set1")[5],
                              "11"=brewer.pal(6, "Set1")[6]))
baselineresd <- scDiffEx(baseline_data, "counts", "subjtype",
                         ntop=nrow(baseline_data), usesig = FALSE,
                         diffexmethod = "DESeq2")

# signatureGeneHeatmap(baseline_data, "logtpm", rownames(sig)[sig$log2FoldChange> 1],
#                      name="DESeq2",
#                      signatureColNames = NULL,
#                      annotationColNames = c("visit", "subjtype"), colList = colList, scale = TRUE,
#                      showRowNames = FALSE)

signatureGeneHeatmap(baseline_data, "logtpm", rownames(baselineresd)[baselineresd$padj< 0.05],
                     name="DESeq2",
                     signatureColNames = NULL,
                     annotationColNames = c("visit", "subjtype"), colList = colList, scale = TRUE,
                     showRowNames = FALSE)

signatureGeneHeatmap(baseline_data, "logtpm", rownames(baselineresd)[baselineresd$padj< 0.05],
                     name="DESeq2",
                     signatureColNames = NULL,
                     annotationColNames = c("flowcell", "lane"), scale = TRUE,
                     showRowNames = FALSE)
```

## Limma (complient only)

```{r diffex_lim2}
baseline_data_complient <- indata_subset[,colData(indata_subset)$visit == "Baseline"]
#only subjects who stay complient
baseline_data_complient <- baseline_data_complient[, !(colData(baseline_data_complient)$Subject %in% as.character(na.omit(colData(indata_subset)$Subject[colData(indata_subset)$totmiss != 0])))]
baseline_data_complient <- baseline_data_complient[rowSds(assay(baseline_data_complient, "counts")) != 0,]
baselineres <- scDiffEx(baseline_data_complient, "logtpm", "subjtype",
                        ntop=nrow(baseline_data_complient), usesig = FALSE,
         diffexmethod = "limma")

res <- lapply(colnames(colData(baseline_data_complient)[,3:16]), function(x){
  return(scDiffEx(baseline_data_complient, "logtpm", "subjtype",
           covariates = x,
           ntop=nrow(baseline_data_complient), usesig = FALSE,
           diffexmethod = "limma"))
})
names(res) <- colnames(colData(baseline_data_complient)[,3:16])
lapply(res, function(x){
  sum(x$padj < 0.05)
})
```

## DESeq2 (complient only)

```{r}
baselineresd <- scDiffEx(baseline_data_complient, "counts", "subjtype",
                         ntop=nrow(baseline_data_complient), usesig = FALSE,
                         diffexmethod = "DESeq2")
signatureGeneHeatmap(baseline_data_complient, "logtpm", rownames(baselineresd)[baselineresd$padj< 0.05],
                     name="DESeq2",
                     signatureColNames = NULL,
                     annotationColNames = c("visit", "subjtype"), colList = colList, scale = TRUE,
                     showRowNames = FALSE)
```

# Pathways {.tabset}

```{r alldata, fig.width=10, fig.height=7, message=FALSE, results='hide'}
make_sig_heatmap_split <- function(sigresults, inputdata, name, scale = FALSE){
  originsigres <- sigresults
  topha1 <- HeatmapAnnotation(
    df = data.frame(colData(inputdata)[paste0(colData(inputdata)$visit, colData(inputdata)$subjtype) %in% "BaselineControl",c("visit","subjtype")]),
    col = list(visit = c("Baseline"="blue", "Month 2"="yellow"),
               subjtype = c("failure"="red", "Control"="grey")),
    height = unit(1, "cm"), show_legend = T, show_annotation_name = FALSE)
  sigresults <- originsigres[,paste0(colData(inputdata)$visit, colData(inputdata)$subjtype) %in% "BaselineControl"]
  if(scale){
    sigresults <- t(scale(t(sigresults)))
  }
  h1 <- Heatmap(sigresults, show_row_names = FALSE, show_column_names = TRUE,
               top_annotation = topha1, name = name)
  topha2 <- HeatmapAnnotation(
    df = data.frame(colData(inputdata)[paste0(colData(inputdata)$visit, colData(inputdata)$subjtype) %in% "Baselinefailure",c("visit","subjtype")]),
    col = list(visit = c("Baseline"="blue", "Month 2"="yellow"),
               subjtype = c("failure"="red", "Control"="grey")),
    height = unit(1, "cm"), show_legend = T, show_annotation_name = FALSE)
  sigresults <- originsigres[,paste0(colData(inputdata)$visit, colData(inputdata)$subjtype) %in% "Baselinefailure"]
  if(scale){
    sigresults <- t(scale(t(sigresults)))
  }
  h2 <- Heatmap(sigresults, show_row_names = FALSE, show_column_names = TRUE,
               top_annotation = topha2, name = name)
  topha3 <- HeatmapAnnotation(
    df = data.frame(colData(inputdata)[paste0(colData(inputdata)$visit, colData(inputdata)$subjtype) %in% "Month 2failure",c("visit","subjtype")]),
    col = list(visit = c("Baseline"="blue", "Month 2"="yellow"),
               subjtype = c("failure"="red", "Control"="grey")),
    height = unit(1, "cm"), show_legend = T, show_annotation_name = TRUE)
  sigresults <- originsigres[,paste0(colData(inputdata)$visit, colData(inputdata)$subjtype) %in% "Month 2failure"]
  if(scale){
    sigresults <- t(scale(t(sigresults)))
  }
  h3 <- Heatmap(sigresults, show_row_names = TRUE, show_column_names = TRUE,
               top_annotation = topha3, name = name)
  draw(h1 + h2 + h3,
       annotation_legend_side="bottom")
}

make_change_in_sig_plot <- function(inputdata, pathwaydata, datatype, scale=FALSE){
  #subset indata to failures
  inputdata <- inputdata[,colData(inputdata)$subjtype == "failure"]
  pathwaydata <- pathwaydata[,colnames(inputdata)]
  if(scale){
    pathwaydata <- t(scale(t(pathwaydata)))
  }
  boxplotdf <- data.frame(t(pathwaydata), Visit=colData(inputdata)$visit, Subject=gsub("\\d$", "", colnames(inputdata)))
  boxplotdfm <- melt(boxplotdf, value.name="Score", variable.name = "Signature", id.vars = c("Visit", "Subject"))
  ggplot(boxplotdfm, aes(x=Visit, y=Score, group=Subject)) +
    geom_point(aes(color=Subject)) +  geom_line(aes(color=Subject)) +
    facet_wrap(~Signature, scales = 'free') +
    ggtitle(datatype)
}
```

## Subset Data (without 102-00107-A0) {.tabset}

```{r subdata, fig.width=10, fig.height=7, message=FALSE, results='hide'}
gsva_res <- runTBsigProfiler(indata_subset, useAssay = "logtpm", algorithm = "GSVA",
                             signatures = TBsignatures,
                             parallel.sz = 4)
ssgsea_res <- runTBsigProfiler(indata_subset, useAssay = "logtpm", algorithm = "ssGSEA",
                               signatures = TBsignatures,
                               parallel.sz = 4)
assign_res <- runTBsigProfiler(indata_subset, useAssay = "logtpm", algorithm = "ASSIGN",
                               signatures = TBsignatures,
                               assignDir = "assignRes_sub")
smokgenes <- readRDS("smokingsig_symbol.rds")
smoking_res <- runTBsigProfiler(indata_subset, useAssay = "logtpm",
                                signatures = list(smoking=smokgenes),
                                algorithm = c("GSVA", "ssGSEA"),
                                combineSigAndAlgorithm = TRUE, parallel.sz = 4)

combinedData <- runTBsigProfiler(indata_subset, useAssay = "logtpm",
                                 algorithm = c("GSVA", "ssGSEA", "ASSIGN"),
                                 signatures = TBsignatures,
                                 assignDir = "assignRes_sub",
                                 combineSigAndAlgorithm = TRUE,
                                 parallel.sz = 4)
```

### Smoking Status

```{r}
colData(smoking_res)$IC_SMOKHX <- factor(colData(smoking_res)$IC_SMOKHX, levels = c("No, never",
                                                                                    "Yes, former",
                                                                                    "Yes, current"))
signatureGeneHeatmap(smoking_res, "logtpm", smokgenes,
                     name="Smoking",
                     signatureColNames = paste(c("GSVA", "ssGSEA"), 
                                               "smoking", sep="_"),
                     annotationColNames = c("IC_SMOKHX", "visit_subjtype"),
                     showRowNames = FALSE, showColumnNames = FALSE)


signatureBoxplot(smoking_res, signatureColNames = c("GSVA_smoking", "ssGSEA_smoking"), name="Smoking",
                 annotationColName = "IC_SMOKHX")

```

### GSVA {.tabset}

#### Heatmap

```{r subgsva_a, fig.width=10, fig.height=8}
signatureHeatmap(gsva_res, name="GSVA", signatureColNames = names(TBsignatures),
                 annotationColNames = c("visit", "subjtype", "totmiss"),
                 colList = colList_m)
```

#### Heatmap Split

```{r subgsva_b, fig.width=10, fig.height=8}
make_sig_heatmap_split(t(as.matrix(colData(gsva_res)[,names(TBsignatures)])), indata_subset, "GSVA")
```

#### Boxplot

```{r subgsva_c, fig.width=10, fig.height=8}
signatureBoxplot(gsva_res, name="GSVA", signatureColNames = names(TBsignatures),
                 annotationColName = c("visit_subjtype"))
```

#### Change in Signature

```{r subgsva_d, fig.width=10, fig.height=8}
make_change_in_sig_plot(indata_subset, t(as.matrix(colData(gsva_res)[,names(TBsignatures)])), "GSVA")
```

#### Delta vs Missed Doses

```{r subgsva_delta, fig.width=10, fig.height=8}
make_diff_vs_annot_scatter <- function(inputdata, pathwaydata, datatype, scale=FALSE){
  #subset indata to failures
  inputdata <- inputdata[,colData(inputdata)$subjtype == "failure"]
  pathwaydata <- pathwaydata[,colnames(inputdata)]
  if(scale){
    pathwaydata <- t(scale(t(pathwaydata)))
  }
  boxplotdf <- data.frame(t(pathwaydata), Visit=colData(inputdata)$visit, Subject=gsub("\\d$", "", colnames(inputdata)), totmiss=colData(inputdata)$totmiss)
  split_bl <- boxplotdf[boxplotdf$Visit == "Baseline",]
  split_2 <- boxplotdf[boxplotdf$Visit != "Baseline",]
  split_bl <- split_bl[split_bl$Subject %in% split_2$Subject,]
  split_2 <- split_2[split_2$Subject %in% split_bl$Subject,]
  diffdf <- split_2[,1:31] - split_bl[,1:31]
  diffdf$totmiss <- split_2$totmiss
  diffdf$Subject <- split_2$Subject
  diffdf <- diffdf[!is.na(diffdf$totmiss),]
  boxplotdfm <- melt(diffdf, value.name="ScoreDelta", variable.name = "Signature", id.vars = c("totmiss", "Subject"))
  ggplot(boxplotdfm, aes(x=totmiss, y=ScoreDelta, group=Subject)) +
    geom_point(aes(color=Subject)) +
    facet_wrap(~Signature, scales = 'free') +
    ggtitle(datatype)
}
make_diff_vs_annot_scatter(gsva_res, t(as.matrix(colData(gsva_res)[,names(TBsignatures)])), "GSVA")
misseddoses <- gsva_res[,colData(gsva_res)$totmiss > 1 & !is.na(colData(gsva_res)$totmiss)]
misseddoses <- gsva_res[,gsub("\\d$", "", colnames(gsva_res)) %in% gsub("\\d$", "", colnames(misseddoses))]
make_change_in_sig_plot(misseddoses, t(as.matrix(colData(misseddoses)[,names(TBsignatures)])), "GSVA")
```

#### Month 2 Non-adherent vs All Baseline

```{r}
#subset data to m2 non-adherent vs all baseline
subset <- gsva_res[,(colData(gsva_res)$visit == "Month 2" & tidyr::replace_na(colData(gsva_res)$totmiss, 0) != 0) | colData(gsva_res)$visit == "Baseline"]
gsvares <- data.frame(colData(subset)[,names(TBsignatures)])

pvalres <- apply(gsvares, 2, function(x){
  return(t.test(x[colData(subset)$visit == "Baseline"],
                x[colData(subset)$visit == "Month 2"])$p.value)
})
which(p.adjust(pvalres, method = "fdr")< 0.05)
names(which(pvalres< 0.05))
signatureBoxplot(subset, signatureColNames = names(which(pvalres< 0.05)), annotationColName = "visit")
pvalres[pvalres< 0.05]
```

#### Basline samples adherent at M2 vs Basline samples non-adherent at M2

```{r}
annotdata <- data.frame(colData(gsva_res))
annotdata <- annotdata[annotdata$visit == "Month 2",]
annotdata <- annotdata[!is.na(annotdata$totmiss),]
adherent <- annotdata$subject[annotdata$totmiss == 0]
nonadherent <- annotdata$subject[annotdata$totmiss != 0]
bl <- gsva_res[,colData(gsva_res)$visit == "Baseline"]
bl <- bl[, colData(bl)$subject  %in% c(adherent, nonadherent)]
colData(bl)$adherent <- ifelse(colData(bl)$subject %in% adherent, "adherent", "non-adherent")

gsvares <- data.frame(colData(bl)[,names(TBsignatures)])

pvalres <- apply(gsvares, 2, function(x){
  return(t.test(x[colData(bl)$adherent == "adherent"],
                x[colData(bl)$adherent == "non-adherent"])$p.value)
})
which(p.adjust(pvalres, method = "fdr")< 0.05)
names(which(pvalres< 0.05))
signatureBoxplot(subset, signatureColNames = names(which(pvalres< 0.05)), annotationColName = "visit")
pvalres[pvalres< 0.05]
```

### Individual Signatures {.tabset}

#### ACS_COR_16

```{r subeachsig1}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[1]],
                     name=names(TBsignatures[1]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[1]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)

signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[1]],
                     name=names(TBsignatures[1]),
                     annotationColNames = c("flowcell"))

signatureGeneHeatmap(gsva_res[,colData(gsva_res)$subjtype=="failure" & tidyr::replace_na(colData(gsva_res)$totmiss, 0) == 0], "logtpm", TBsignatures[[1]],
                     name=names(TBsignatures[1]), showColumnNames = FALSE,
                     signatureColNames = paste(names(TBsignatures[1]), sep="_"),
                     annotationColNames = c("visit"), colList = colList[1])
```

#### Anderson_TB_vs_LTBI_42

```{r subeachsig2}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[2]],
                     name=names(TBsignatures[2]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[2]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Anderson_TB_vs_other_LTBI_51

```{r subeachsig3}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[3]],
                     name=names(TBsignatures[3]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[3]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Berry_393

```{r subeachsig4}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[4]],
                     name=names(TBsignatures[4]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[4]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Berry_86

```{r subeachsig5}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[5]],
                     name=names(TBsignatures[5]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[5]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Blankley_380

```{r subeachsig6}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[6]],
                     name=names(TBsignatures[6]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[6]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Blankley_5

```{r subeachsig7}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[7]],
                     name=names(TBsignatures[7]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[7]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Bloom_140

```{r subeachsig8}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[8]],
                     name=names(TBsignatures[8]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[8]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### DISEASE_9

```{r subeachsig9}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[9]],
                     name=names(TBsignatures[9]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[9]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Esmail_subclinical_203

```{r subeachsig10}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[10]],
                     name=names(TBsignatures[10]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[10]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Esmail_subclinical_82

```{r subeachsig11}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[11]],
                     name=names(TBsignatures[11]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[11]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Esmail_TB_vs_LTBI_893

```{r subeachsig12}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[12]],
                     name=names(TBsignatures[12]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[12]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### FAILURE_13

```{r subeachsig13}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[13]],
                     name=names(TBsignatures[13]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[13]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Jacobsen_3

```{r subeachsig14}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[14]],
                     name=names(TBsignatures[14]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[14]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Kaforou_TB_vs_LTBI_27

```{r subeachsig15}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[15]],
                     name=names(TBsignatures[15]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[15]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Kaforou_TB_vs_LTBI_other_53

```{r subeachsig16}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[16]],
                     name=names(TBsignatures[16]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[16]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Kaforou_TB_vs_other_44

```{r subeachsig17}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[17]],
                     name=names(TBsignatures[17]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[17]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Lee_4

```{r subeachsig18}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[18]],
                     name=names(TBsignatures[18]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[18]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Maertzdorf_100

```{r subeachsig19}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[19]],
                     name=names(TBsignatures[19]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[19]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Maertzdorf_4

```{r subeachsig20}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[20]],
                     name=names(TBsignatures[20]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[20]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Predict29

```{r subeachsig21}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[21]],
                     name=names(TBsignatures[21]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[21]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### RESPONSE5

```{r subeachsig22}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[22]],
                     name=names(TBsignatures[22]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[22]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Roe_4

```{r subeachsig23}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[23]],
                     name=names(TBsignatures[23]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[23]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Sambarey_10

```{r subeachsig24}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[24]],
                     name=names(TBsignatures[24]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[24]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Singhania_20

```{r subeachsig25}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[25]],
                     name=names(TBsignatures[25]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[25]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Sloot_2

```{r subeachsig26}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[26]],
                     name=names(TBsignatures[26]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[26]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Suliman_RISK4

```{r subeachsig27}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[27]],
                     name=names(TBsignatures[27]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[27]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Sweeney_DIAG3

```{r subeachsig28}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[28]],
                     name=names(TBsignatures[28]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[28]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Walter_TB_vs_LTBI_51

```{r subeachsig29}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[29]],
                     name=names(TBsignatures[29]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[29]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Walter_TB_vs_Pneumonia_47

```{r subeachsig30}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[30]],
                     name=names(TBsignatures[30]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[30]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```

#### Walter_TB_vs_Pneumonia_LTBI_119

```{r subeachsig31}
signatureGeneHeatmap(combinedData, "logtpm", TBsignatures[[31]],
                     name=names(TBsignatures[31]),
                     signatureColNames = paste(c("GSVA", "ssGSEA", "ASSIGN"), 
                                               names(TBsignatures[31]), sep="_"),
                     annotationColNames = c("visit", "subjtype"), colList = colList)
```
